### 2021-09-27 paper/main.tex
Update manuscript

\usepackage{acronym}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbold}
\usepackage{booktabs}
\usepackage{color}
\usepackage{fontawesome}
\usepackage{graphics}
\usepackage{microtype}
\usepackage{nicefrac}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{dsfont}
\usepackage{tcolorbox}

\newtcolorbox{custombox}[1][]
{
  colframe=blue!40,
  colback=blue!8,
  left=2pt,
  right=2pt,
  top=2pt,
  bottom=2pt,
  \centering #1
}

@@

\begin{custombox}
{\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations. This pathology tends to be accentuated when using a small simulation-budget in both amortized and non-amortized approaches.

@@

% Appendix
\FloatBarrier
\newpage
\appendix

>>>>

\usepackage{acronym}
\usepackage{amsfonts}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbold}
\usepackage{booktabs}
\usepackage{color}
\usepackage{graphics}
\usepackage{microtype}
\usepackage{nicefrac}
\usepackage{caption}
\usepackage{float}
\usepackage{tcolorbox}

\newtcolorbox{custombox}[1][]
{
  colframe=blue!40,
  colback=blue!8,
  left=2pt,
  right=2pt,
  top=2pt,
  bottom=2pt,
  #1
}

@@

\protect\begin{custombox}
{\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations. This pathology tends to be accentuated when using a small simulation-budget in both amortized and non-amortized approaches.

@@

% Appendix
\clearpage
\newpage
\appendix
